---
title: "Trustpilot Dynamic Funnel Analysis"
output: 
  flexdashboard::flex_dashboard:
    theme: flatly
    orientation: columns
runtime: shiny
---

```{r global, include = FALSE}

## Load libraries ---------------------

library(glue)
library(tidyverse)
library(plotly)
library(magrittr)
library(flexdashboard)
library(lubridate)
library(DT)
library(hjplottools)
library(zoo)
library(here)

## Set options ------------------------

options(scipen = 999)

## Load data --------------------------

full_data <- read_csv(here("03.Data", "trustpilot_funnel_data.csv"))

```

```{r Generate Regression Output, include = FALSE}

## Regression 1 (search ~ prompted_awareness, UK)
reg_1_uk <- full_data %>%
  filter(country == "UK") %$%
  lm(search ~ prompted_awareness + I(prompted_awareness^2))

## Regression 2 (consumer_users ~ search, UK)
reg_2_uk <- full_data %>%
  filter(country == "UK") %$%
  lm(consumer_users ~ search)

## Regression 3 (traffic ~ consumer_users, UK)
reg_3_uk <- full_data %>%
  filter(country == "UK") %$%
  lm(biz_traffic_consumer ~ consumer_users)

## Regression 4 (consumer_leads ~ traffic, UK)
reg_4_uk <- full_data %>%
  filter(country == "UK") %$%
  lm(consumer_leads ~ biz_traffic_consumer)

## Regression 1 (search ~ prompted_awareness, UK)
reg_1_it <- full_data %>%
  filter(country == "IT") %$%
  lm(search ~ prompted_awareness)

## Regression 2 (consumer_users ~ search, UK)
reg_2_it <- full_data %>%
  filter(country == "IT") %$%
  lm(consumer_users ~ search + I(search^2) +
       I(search^3))

## Regression 3 (traffic ~ consumer_users, UK)
reg_3_it <- full_data %>%
  filter(country == "IT") %$%
  lm(biz_traffic_consumer ~ consumer_users)

## Regression 4 (consumer_leads ~ traffic, UK)
reg_4_it <- full_data %>%
  filter(country == "IT") %$%
  lm(consumer_leads ~ biz_traffic_consumer)

```

```{r Functions to Generate Values}

search_generate_uk <- function(promp_aware_est) {
  reg_1_uk$coefficients[["(Intercept)"]] +
    (reg_1_uk$coefficients[['prompted_awareness']] * promp_aware_est) +
    (reg_1_uk$coefficients[['I(prompted_awareness^2)']] * I(promp_aware_est^2))
}

consumer_users_generate_uk <- function(search_est) {
  reg_2_uk$coefficients[["(Intercept)"]] +
    (reg_2_uk$coefficients[['search']] * search_est)
}

biz_traffic_generate_uk <- function(consumer_users_est) {
  reg_3_uk$coefficients[["(Intercept)"]] +
    (reg_3_uk$coefficients[['consumer_users']] * consumer_users_est)
}

consumer_leads_generate_uk <- function(biz_traffic_est) {
  reg_4_uk$coefficients[["(Intercept)"]] +
    (reg_4_uk$coefficients[["biz_traffic_consumer"]] * biz_traffic_est)
}

search_generate_it <- function(promp_aware_est) {
  reg_1_it$coefficients[["(Intercept)"]] +
    (reg_1_it$coefficients[['prompted_awareness']] * promp_aware_est)
}

consumer_users_generate_it <- function(search_est) {
  reg_2_it$coefficients[["(Intercept)"]] +
    (reg_2_it$coefficients[['search']] * search_est) +
    (reg_2_it$coefficients[['I(search^2)']] * I(search_est^2)) +
    (reg_2_it$coefficients[['I(search^3)']] * I(search_est^3))
}

biz_traffic_generate_it <- function(consumer_users_est) {
  reg_3_it$coefficients[["(Intercept)"]] +
    (reg_3_it$coefficients[['consumer_users']] * consumer_users_est)
}

consumer_leads_generate_it <- function(biz_traffic_est) {
  reg_4_it$coefficients[["(Intercept)"]] +
    (reg_4_it$coefficients[["biz_traffic_consumer"]] * biz_traffic_est)
}

```

```{r Nice Number Function}

rnd_num <- function(x) {prettyNum(round(x, 2), big.mark = ",")}
nice_num <- function(x) {prettyNum(round(x, 0), big.mark = ",")}

```

Funnel Analysis Overview
=======================================================================

Column {data-width = 500}
-----------------------------------------------------------------------

```{r}

img(src = "02.Documentation/funnel_design.png")

```

Column {data-width = 500}
-----------------------------------------------------------------------


Funnel Design - UK
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

sliderInput("prompted_awareness_uk", label = "Prompted Brand Awareness",
            min = 0.50, max = 0.9, value = 0.5, step = 0.01)

```

Column {.tabset}
-----------------------------------------------------------------------

### Complete Funnel

```{r}

renderPlotly({
  
  ## Generate intercepts
  promp_aware_est <- input$prompted_awareness_uk
  search_est <- search_generate_uk(promp_aware_est)
  consumer_users_est <- consumer_users_generate_uk(search_est)
  biz_traffic_est <- biz_traffic_generate_uk(consumer_users_est)
  consumer_leads_est <- consumer_leads_generate_uk(biz_traffic_est)
  
  
  elements <- c("Prompted Brand Awareness", "Search", "Consumer Site Users (000s)",
                "Business Traffic (from Consumer Site, 000s)", "Leads (000s)")
  
  funnel_values <- c(round(promp_aware_est, 2),
                     round(search_est, 2),
                     round(consumer_users_est / 1000000, 2),
                     round(biz_traffic_est / 10000, 2),
                     round(consumer_leads_est / 1000, 2))
  
  funnel_labels <-
    c(glue("Prompted Awareness: ", rnd_num(promp_aware_est)),
      glue("Share of Search: ", rnd_num(search_est)),
      glue("Consumer Site Users: ", nice_num(consumer_users_est)),
      glue("Business Traffic (from Consumer Site): ",
           nice_num(biz_traffic_est)),
      glue("Leads: ", nice_num(consumer_leads_est)))
  
  plot_ly(hovertext = "test",
          hoverinfo = "text") %>%
    add_trace(type = "funnel",
              text = funnel_labels,
              x = funnel_values,
              marker = list(color = c("deepskyblue", "deepskyblue",
                                      "deepskyblue", "deepskyblue",
                                      "deepskyblue"))) %>%
    layout(yaxis = list(categoryarray = elements))
  
})

```

### Chart A: Effect of Brand Awareness on Share of Search

```{r} 

## Create plot

renderPlot({
  
  ## Generate estimates for search
  ## (given the user-input value of prompted brand awareness)
  promp_aware_est <- input$prompted_awareness_uk
  search_est <- search_generate_uk(promp_aware_est)
  
  ## Create intersection label
  intersection_label <- glue("Prompted Awareness: ", promp_aware_est,
                             "\nSearch: ", rnd_num(search_est))
  
  ## Create plot
  full_data %>%
    filter(country == "UK") %>%
    
    ## Create plot of prompted_awareness against search
    ggplot(aes(x = prompted_awareness, y = search)) +
    geom_smooth(method = 'lm',
                formula = y ~ x + I(x^2),
                colour = "red",
                se = TRUE) +
    geom_point() +
    labs(x = "\nPrompted Awarness",
         y = "Search\n",
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_1_uk)$adj.r.squared))) +
    xlim(0.43, 0.75) +
    
    ## Add dynamic intersection lines
    geom_segment(aes(x = promp_aware_est, y = -Inf,
                     xend = promp_aware_est, yend = search_est)) +
    geom_segment(aes(x = -Inf, y = search_est,
                     xend = promp_aware_est, yend = search_est)) +
    geom_point(x = promp_aware_est, y = search_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    annotate(geom = "label",
             x = promp_aware_est, y = search_est,
             label = intersection_label,
             fill = "green") +
    
    hj_theme()
  
})

```

#### Include text as well

### Chart B: Effect of Share of Search on Customer Site Users

```{r}

renderPlot({
  
  ## Generate estimates for search and consumer users
  ## (given the user-input value of prompted brand awareness)
  promp_aware_est <- input$prompted_awareness_uk
  search_est <- search_generate_uk(promp_aware_est)
  consumer_users_est <- consumer_users_generate_uk(search_est)
  
  ## Create intersection label
  intersection_label <- 
    glue("Search: ", rnd_num(search_est),
         "\nConsumer Website Users: ", nice_num(consumer_users_est))
  
  ## Create plot
  full_data %>%
    filter(country == "UK") %>%
    
    ## Generate plot of search against consumer website users
    ggplot(aes(x = search, y = consumer_users)) +
    geom_smooth(method = 'lm',
                formula = y ~ x,
                colour = "red",
                se = TRUE) +
    geom_point() +
    labs(x = "\nSearch",
         y = "Consumer Website Users (Monthly)\n",
         caption = glue("Adjusted R Squared: ",
                         rnd_num(summary(reg_2_uk)$adj.r.squared))) +
    
    ## Add dynamic intersection lines
    geom_segment(aes(x = search_est, y = -Inf,
                     xend = search_est, yend = consumer_users_est)) +
    geom_segment(aes(x = -Inf, y = consumer_users_est,
                     xend = search_est, yend = consumer_users_est)) +
    geom_point(x = search_est, y = consumer_users_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    geom_label(aes(x = search_est, y = consumer_users_est,
                  label = intersection_label),
              fill = "green",
              nudge_y = 200000) +
    
    hj_theme()
})

```

### Chart C: Effect of Customer Site Users on Business Site Traffic

```{r}

renderPlot({
  
  ## Generate estimates for search, consumer users and business traffic
  ## (given the user-input value of prompted brand awareness)
  promp_aware_est <- input$prompted_awareness_uk
  search_est <- search_generate_uk(promp_aware_est)
  consumer_users_est <- consumer_users_generate_uk(search_est)
  biz_traffic_est <- biz_traffic_generate_uk(consumer_users_est)
  
  ## Generate intersection label
  intersection_label <- 
    glue("Consumer Website Users: ",
         nice_num(consumer_users_est),
         "\nBusiness Site Traffic (from Consumer Website): ",
         nice_num(biz_traffic_est))
  
  ## Create plot
  full_data %>%
    filter(country == "UK") %>%
    ggplot(aes(x = consumer_users, y = biz_traffic_consumer)) +
    geom_smooth(method = 'lm',
                formula = y ~ x,
                colour = "red",
                se = TRUE) +
    geom_point() +
    labs(x = "\nConsumer Website Users (Monthly)",
         y = "Business Site Traffic (from Consumer Site)\n",
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_3_uk)$adj.r.squared))) +
    
    ### Add dynamic intersection input
    geom_segment(aes(x = consumer_users_est, y = -Inf,
                     xend = consumer_users_est, yend = biz_traffic_est)) +
    geom_segment(aes(x = -Inf, y = biz_traffic_est,
                     xend = consumer_users_est, yend = biz_traffic_est)) +
    geom_point(x = consumer_users_est, y = biz_traffic_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    annotate(geom = "label",
             x = consumer_users_est, y = biz_traffic_est,
             label = intersection_label,
             fill = "green") +
    
    hj_theme()
})

```

### Chart D: Effect of Business Site Traffic on Leads

```{r}

renderPlot({
  
  ## Generate estimates for search, consumer users, business traffic and
  ## leads (given the user-input value of prompted brand awareness)
  promp_aware_est <- input$prompted_awareness_uk
  search_est <- search_generate_uk(promp_aware_est)
  consumer_users_est <- consumer_users_generate_uk(search_est)
  biz_traffic_est <- biz_traffic_generate_uk(consumer_users_est)
  consumer_leads_est <- consumer_leads_generate_uk(biz_traffic_est)
  
  ## Generate intersection label
  intersection_label <- glue("Business Site Traffic (from Consumer Site): ",
                             nice_num(biz_traffic_est),
                             "\nLeads (from Consumer Site): ",
                             nice_num(consumer_leads_est))
  
  ## Generate plot of business site traffic (from consumer site) against
  ## leads
  full_data %>%
    filter(country == "UK") %>%
    ggplot(aes(x = biz_traffic_consumer, y = consumer_leads)) +
    geom_smooth(method = 'lm',
                formula = y ~ x,
                colour = "red",
                se = TRUE) +
    geom_point() +
    labs(x = "\nBusiness Site Traffic (from Consumer Site)",
         y = glue("Leads Generated from Consumer Site\n\\
                  (Free Sign-ups and Demo Requests)\n"),
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_4_uk)$adj.r.squared))) +
    
    ## Add dynamic intersection input
    geom_segment(aes(x = biz_traffic_est, y = -Inf,
                     xend = biz_traffic_est, yend = consumer_leads_est)) +
    geom_segment(aes(x = -Inf, y = consumer_leads_est,
                     xend = biz_traffic_est, yend = consumer_leads_est)) +
    geom_point(x = biz_traffic_est, y = consumer_leads_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    geom_label(aes(x = biz_traffic_est, y = consumer_leads_est),
               label = intersection_label,
               fill = "green",
               nudge_y = 150) +
    
    hj_theme()
})

```


Funnel Design - IT
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

sliderInput("prompted_awareness_it", label = "Prompted Brand Awareness",
            min = 0.3, max = 0.8, value = 0.3, step = 0.01)

```

Column {.tabset}
-----------------------------------------------------------------------

### Complete Funnel

```{r}

renderPlotly({
  
  ## Generate intercepts
  promp_aware_est <- input$prompted_awareness_it
  search_est <- search_generate_it(promp_aware_est)
  consumer_users_est <- consumer_users_generate_it(search_est)
  biz_traffic_est <- biz_traffic_generate_it(consumer_users_est)
  consumer_leads_est <- consumer_leads_generate_it(biz_traffic_est)
  
  elements <- c("Prompted Awareness", "Share of Search", "Consumer Sessions",
                "Business Site Traffic")
  
  funnel_values <- c(round(promp_aware_est, 2),
                     round(search_est, 2),
                     round(consumer_users_est / 1000000, 2),
                     round(biz_traffic_est / 10000, 2),
                     round(consumer_leads_est / 1000, 2))
  
  funnel_labels <-
    c(glue("Prompted Awareness: ", rnd_num(promp_aware_est)),
      glue("Share of Search: ", rnd_num(search_est)),
      glue("Consumer Site Users: ", nice_num(consumer_users_est)),
      glue("Business Traffic (from Consumer Site): ",
           nice_num(biz_traffic_est)),
      glue("Leads: ", nice_num(consumer_leads_est)))
  
  plot_ly() %>%
    add_trace(type = "funnel",
              #text = funnel_labels,
              #y = elements,
              x = funnel_values,
              marker = list(color = c("deepskyblue", "deepskyblue",
                                      "deepskyblue", "deepskyblue",
                                      "deepskyblue"))) %>%
    layout(yaxis = list(categoryarray = elements))
  
})

```

### Chart A: Effect of Brand Awareness on Share of Search

```{r} 

## Create plot

renderPlot({
  ## Generate intercepts
  promp_aware_est <- input$prompted_awareness_it
  search_est <- search_generate_it(promp_aware_est)
  
  ## Generate intersection label
  intersection_label <- glue("Prompted Awareness: ", promp_aware_est,
                             "\nSearch: ", rnd_num(search_est))
  
  ## Create plot
  full_data %>%
    filter(country == "IT") %>%
    
    ## Create plot of prompted_awareness against search
    ggplot(aes(x = prompted_awareness, y = search)) +
    geom_smooth(method = 'lm',
                formula = y ~ x,
                colour = "red",
                se = F) +
    geom_point() +
    labs(x = "\nPrompted Awarness",
         y = "Search\n",
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_1_it)$adj.r.squared))) +
    
    ## Add dynamic intersection lines
    geom_segment(aes(x = promp_aware_est, y = -Inf,
                     xend = promp_aware_est, yend = search_est)) +
    geom_segment(aes(x = -Inf, y = search_est,
                     xend = promp_aware_est, yend = search_est)) +
    geom_point(x = promp_aware_est, y = search_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    geom_label(aes(x = promp_aware_est, y = search_est),
               label = intersection_label,
               fill = "green",
               nudge_y = 0.04) +
    
    hj_theme()
})

```

### Chart B: Effect of Share of Search on Customer Site Users

```{r}

renderPlot({
  
  ## Generate intercepts for search and consumer users
  promp_aware_est <- input$prompted_awareness_it
  search_est <- search_generate_it(promp_aware_est)
  consumer_users_est <- consumer_users_generate_it(search_est)
  
  ## Create intersection label
  intersection_label <- glue("Share of Search: ",
                             rnd_num(search_est),
                             "\nUnique Users: ",
                             nice_num(consumer_users_est))
  
  ## Create plot
  full_data %>%
    filter(country == "IT") %>%
    ggplot(aes(x = search, y = consumer_users)) +
    geom_smooth(method = 'lm',
                formula = y ~ x + I(x^2) + I(x^3),
                colour = "red",
                se = F) +
    geom_point() +
    labs(x = "\nSearch",
         y = "Consumer Website Users (Monthly)\n",
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_2_it)$adj.r.squared))) +
    
    ## Add dynamic intersection lines
    geom_segment(aes(x = search_est, y = -Inf,
                     xend = search_est, yend = consumer_users_est)) +
    geom_segment(aes(x = -Inf, y = consumer_users_est,
                     xend = search_est, yend = consumer_users_est)) +
    geom_point(x = search_est, y = consumer_users_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    geom_label(aes(x = search_est, y = consumer_users_est),
               label = intersection_label,
               fill = "green",
               nudge_y = 100000) +
    
    hj_theme()
})

```

### Chart C: Effect of Customer Site Users on Business Site Traffic

```{r}

renderPlot({
  
  ## Generate intercepts fir search, consumer users and business site traffic
  promp_aware_est <- input$prompted_awareness_it
  search_est <- search_generate_it(promp_aware_est)
  consumer_users_est <- consumer_users_generate_it(search_est)
  biz_traffic_est <- biz_traffic_generate_it(consumer_users_est)
  
  ## Create intersection label
  intersection_label <-
    glue("Consumer Website Sessions (Monthly): ",
         nice_num(consumer_users_est),
         "\nBusiness Site Traffic (from Consumer Website): ",
         nice_num(biz_traffic_est))
  
  ## Create plot
  full_data %>%
    filter(country == "IT") %>%
    
    ## Generate plot of consumer_users against business site traffic (from
    ## customer site)
    ggplot(aes(x = consumer_users, y = biz_traffic_consumer)) +
    geom_smooth(method = 'lm',
                formula = y ~ x,
                colour = "red",
                se = F) +
    geom_point() +
    labs(x = "Consumer Website Sessions (Monthly)",
         y = "Business Site Traffic (from Consumer Site)",
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_3_it)$adj.r.squared))) +
    
    ## Add dynamic intersection input
    geom_segment(aes(x = consumer_users_est, y = -Inf,
                     xend = consumer_users_est, yend = biz_traffic_est)) +
    geom_segment(aes(x = -Inf, y = biz_traffic_est,
                     xend = consumer_users_est, yend = biz_traffic_est)) +
    geom_point(x = consumer_users_est, y = biz_traffic_est,
               colour = "purple", size = 5) +
    
    ## Add intersection label
    geom_label(aes(x = consumer_users_est, y = biz_traffic_est),
              label = intersection_label,
              fill = "green",
              nudge_y = 400) +
    
    hj_theme()
})

```

### Chart D: Effect of Business Site Traffic on Leads

```{r}

renderPlot({
  
  ## Generate intercepts for search, consumer users, business site traffic
  ## and leads
  promp_aware_est <- input$prompted_awareness_it
  search_est <- search_generate_it(promp_aware_est)
  consumer_users_est <- consumer_users_generate_it(search_est)
  biz_traffic_est <- biz_traffic_generate_it(consumer_users_est)
  consumer_leads_est <- consumer_leads_generate_it(biz_traffic_est)
  
  ## Generate intersection label
  intersection_label <- glue("Business Site Traffic (from Consumer Site): ",
                             nice_num(biz_traffic_est),
                             "\nLeads (from Consumer Site): ",
                             nice_num(consumer_leads_est))
  
  ## Generate plot of business traffic (from consumer site) against
  ## consumer_leads
  full_data %>%
    filter(country == "IT") %>%
    ggplot(aes(x = biz_traffic_consumer, y = consumer_leads)) +
    geom_smooth(method = 'lm',
                formula = y ~ x,
                colour = "red",
                se = F) +
    geom_point() +
    labs(x = "\nBusiness Site Traffic from Consumer Site",
         y = glue("Leads Generated from Consumer Site\n\\
                  (Free Sign-ups and Demo Requests)"),
         caption = glue("Adjusted R Squared: ",
                        rnd_num(summary(reg_4_it)$adj.r.squared))) +
    
    ## Add dynamic intersection input
    geom_segment(aes(x = biz_traffic_est, y = -Inf,
                     xend = biz_traffic_est, yend = consumer_leads_est)) +
    geom_segment(aes(x = -Inf, y = consumer_leads_est,
                     xend = biz_traffic_est, yend = consumer_leads_est)) +
    geom_point(x = biz_traffic_est, y = consumer_leads_est,
               colour = "purple", size = 5) +
    
    ## Add label to intersection
    geom_label(aes(x = biz_traffic_est, y = consumer_leads_est),
               fill = "green",
               label = intersection_label,
               nudge_y = 20) +
    
    hj_theme()
})

```



Metric Comparisons
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

input_options <-
  c("Prompted Brand Awareness" = "prompted_awareness",
    "Search" = "search",
    "Consumer Users" = "consumer_users",
    "Consumer Sessions" = "consumer_users",
    "All Leads (from Consumer Website)" = "all_consumer_leads",
    "Free Sign-up and Demo Request Leads (All Channels)" = "all_leads",
    "Free Sign-up and Demo Request Leads (Consumer Site)" = "consumer_leads")

selectInput("trustpilot_region", label = "Select Country",
            choices = c("UK", "IT"))

selectInput("comp-x", label = "X-Axis Metric", choices = input_options)

selectInput("comp-y", label = "Y-Axis Metric", choices = input_options)

#sliderInput("prompted_awareness", label = "Prompted Brand Awareness",
#              min = 0.2, max = 0.8, value = 0.5, step = 0.01)

```

Column
-----------------------------------------------------------------------

### Chart

```{r} 

## Create plot

renderPlot({
  
  ## Create plot
  full_data %>%
    filter(country == input$trustpilot_region) %>%
    ggplot(aes_string(x = input$`comp-x`, y = input$`comp-y`)) +
    geom_smooth(method = 'lm', formula = y ~ x, colour = "red") +
    geom_point() +
    hj_theme() +
    scale_y_continuous(labels = function(x) {
      nice_num(x)
    })
})

```


Funnel Data
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

selectInput("trustpilot_region_data", label = "Select Country",
            choices = c("UK", "IT"))

dateRangeInput("table_dates", "Select Dates",
               start = "2017-01-01",
               end = "2022-03-01",
               min = "2017-01-01",
               max = "2022-03-01",
               format = "MM yyyy",
               startview = "year")

checkboxGroupInput(
  "table_variables", "Select Variables for Comparison",
  choices = c("Prompted Brand Awareness",
              "Share of Search",
              "Unique Consumer Website Users",
              "Unique Consumer Website sessions",
              "Business Page Loads (from Consumer Website)",
              "All Leads (from Consumer Website)",
              "Free Signup and Demo Request Leads (All Channels)",
              "Free Signup and Demo Request Leads (Consumer Site)",
              "Deals Won",
              "Retention"),
  selected = c("Prompted Brand Awareness",
               "Share of Search",
               "Unique Consumer Website sessions",
               "Business Page Loads (from Consumer Website)",
               "Free Signup and Demo Request Leads (Consumer Site)")
)

```

Column
-----------------------------------------------------------------------

```{r}

renderTable({
  
  full_data %>%
    filter(country == input$trustpilot_region_data,
           month_start >= input$table_dates[1]) %>%
    
    mutate(Month = format(month_start, "%B %Y"),
           deals_won = as.integer(deals_won)) %>%
    select(-c(month_start, month, year, renewal_rate,
              price_expansion, net_renewal_rate, country)) %>%
    
    relocate(Month) %>%
    relocate(prompted_awareness, .after = Month) %>%
    relocate(search, .after = prompted_awareness) %>%
    relocate(consumer_users, .after = search) %>%
    relocate(consumer_users, .after = consumer_users) %>%
    relocate(biz_traffic_consumer, .after = consumer_users) %>%
    relocate(all_consumer_leads, .after = biz_traffic_consumer) %>%
    relocate(all_leads, .after = all_consumer_leads) %>%
    relocate(consumer_leads, .after = all_leads) %>%
    relocate(deals_won, .after = consumer_leads) %>%
    
    mutate(across(.cols = c(consumer_users, consumer_users,
                            biz_traffic_consumer, all_consumer_leads, all_leads,
                            consumer_leads, retention),
                  nice_num),
           across(.cols = c(consumer_users, consumer_users,
                            biz_traffic_consumer, all_consumer_leads, all_leads,
                            consumer_leads, retention),
                  ~ case_when(. == "NA" ~ "-",
                              TRUE ~ .))) %>%
    
    rename(
      `Prompted Brand Awareness` = prompted_awareness,
      `Share of Search` = search,
      `Unique Consumer Website Users` = consumer_users,
      `Unique Consumer Website sessions` = consumer_users,
      `Business Page Loads (from Consumer Website)` = biz_traffic_consumer,
      `All Leads (from Consumer Website)` = all_consumer_leads,
      `Free Signup and Demo Request Leads (All Channels)` = all_leads,
      `Free Signup and Demo Request Leads (Consumer Site)` = consumer_leads,
      `Deals Won` = deals_won,
      `Retention` = retention
    ) %>%
    
    select(Month,
           input$table_variables)
  
}, striped = TRUE, align = 'l', na = '-')

```


